---
title: "A"
output: html_notebook
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Inputs and outputs

input data = the"what" that is manipulated
parameters determine "how" the manipulation is done

# Example 1 power generation 

the function can use variables that do not interrupt with other variables of your code of somelses' code 
Anything that is defined whitin the functuion does not exit outside the function 

```{r}
power_gen = function (height, flow, rho = 1000, g = 9.8, K = 0.8){
  result = rho * height * flow * g * K
  return(result)
}
```

## Error checking 

The function will work with whaterver your are giving, so is helpful to provide a warmming message to let know the user that he/she is using an inadequate value.

example:

if (height < 0) return (NA) -- In that way the user can be aware 

## Documentation

You have to save the function as a separate file and create documentation 

# Example 2 -- power required to keep a car moving at a given speed

```{r}
power_car = function (V, mass, g = 9.8, Pair = 1.2, Crolling = 0.015, Cdrag = 0.3){
  pb =  (Crolling * mass * g * V + (0.5 * Pair * Cdrag * (V^3)))
  return(pb)
}
```

